Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-12-21 patchy-selection-paper.tex
hours of latex-ing later, resubmitted

@@

\ifsubmissionversion
    \usepackage[tablesfirst]{endfloat}
    \usepackage{cite}
    % Use the PLoS provided bibtex style
    \bibliographystyle{plos2009}
    \newcommand{\citep}[1]{\cite{#1}}
    \newcommand{\citet}[1]{\cite{#1}}
\else
    \usepackage{natbib}
    \bibliographystyle{abbrvnat}
\fi

\ifsubmissionversion
% \linespread{1.6}
%\usepackage{setspace} 
%\doublespacing
\fi

@@

\pagestyle{myheadings}
%% ** EDIT HERE **

@@

%%%%%%%%%%%
\abstract{
Species often encounter, and adapt to, many patches of locally similar environmental conditions across their range. 
Such adaptation can occur through convergent evolution if different alleles arise and spread in different patches, 
or through the spread of shared alleles by migration
acting to synchronize adaptation across the species.
The tension between the two reflects 
the degree of constraint imposed on evolution by the underlying genetic architecture 
versus how effectively selection and geographic isolation act to inhibit the geographic spread of locally adapted alleles.
This paper studies a model of the balance between these two routes to adaptation in continuous environments with patchy selection pressures.
We address the following questions: 
How long does it take for a novel, locally adapted allele to appear in a
patch of habitat where it is favored through mutation?
Or, through migration from another, already adapted patch?
Which is more likely to occur, as a function of distance between the patches?
How can we tell which has occurred, i.e.\ what population genetic
signal is left by the spread of migrant alleles?
To answer these questions we examine the family structure underlying migration--selection equilibrium
surrounding an already adapted patch,
in particular treating those rare families that reach new patches
as spatial branching processes.
This provides a way to understand the role of geographic separation between patches 
in promoting convergent adaptation and the genomic signals it leaves behind.
We illustrate these ideas using the convergent evolution of cryptic coloration in the rock pocket mouse, \textit{Chaetodipus intermedius}, as an empirical example.

\textbf{Author Summary:}
Often, a large species range will include patches where the species differs because it has adapted to locally differing conditions.
For instance, rock pocket mice are often found with a coat color that matches the rocks they live in,
these color differences are controlled genetically,
and mice that don't match the local rock color are more likely to be eaten by predators.
Sometimes, similar genetic changes have occurred independently in different patches,
suggesting that there were few accessible ways to evolve the locally adaptive form.
However, the genetic basis could also be shared if
migrants carry the locally beneficial genotypes between nearby patches,
despite being at a disadvantage between the patches.
We use a mathematical model of random migration to determine how quickly adaptation is expected to occur 
through new mutation and through migration from other patches,
and study in more detail what we would expect successful migrations between patches to look like.
The results are useful for determining whether similar adaptations in different locations are likely to have the same genetic basis or not,
and more generally in understanding how species adapt to patchy, heterogeneous landscapes.
}

@@

\subsection*{Acknowledgements}
We would like to heartily thank Joachim Hermisson for a number of insightful suggestions,
and catching the algebra error present in the first version of this paper on the bioRxiv,
as well as the two anonymous reviewers.
We would also like to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.

@@

Here (and at other parameter choices) we see that the probability of establishment $p(x)$ goes to the equilibrium value
(approximately $p_e = 2s/\xi^2$) within the patch;
the transition is fairly symmetrical about the edge of the patch, even if the edge of the patch is not sharp.
The fit is equally good for other parameter values,
even if migration can move further than one deme and offspring numbers are not Poisson (results not shown).
This lends credence to our approximation that the integral of $p(x)$ over the entire range
is close to $p_e$ multiplied by the area of the patch.

@@

@@

\appendix

@@

%%%%%%%
\section{The exact solution to the equilibrium frequency}
\label{apx:elliptic_integrals}

@@

%%%%%%%
\section{More information about the simulations}
\label{apx:parameter_tables}

@@

@@

\section*{Supplemental material}

% restart figure and table numbering
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}

\begin{figure}
  \begin{center}
    \includegraphics{mutation-times-predicted}
  \end{center}
  \caption{
    The same data shown in the left panel of figure~\ref{fig:sim_times},
    but all times shown (not just the interquartile ranges),
    and including those parameter values at which most of the simulations did not adapt by 25,000 generations.
  } \label{sfig:sim_migration_times}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics{migration-time-predicted}
  \end{center}
  \caption{
    The same data shown in the right panel of figure~\ref{fig:sim_times},
    but all times shown (not just the interquartile ranges),
    and including those parameter values at which most of the simulations did not adapt by 25,000 generations.
    The upper panel has the predicted time to adaptation on the horizontal axis as in figure~\ref{fig:sim_times},
    and the lower panel has, for comparison, the raw distance between patches 
    (which predicts time to adaptation, but not as well).
  } \label{sfig:sim_mutation_times}
\end{figure}

@@

% sm=0.1
\begin{figure}
  \begin{center}
    \includegraphics{example-mutation-sims/18885-r1-501-sb0_01-sm-0_1-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/56325-r1-501-sb0_01-sm-0_1-N600-pophistory-run}
    \includegraphics{example-mutation-sims/28432-r1-501-sb0_01-sm-0_1-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by new mutation
    with $s_m=0.1$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_1}
\end{figure}

% sm=0.01
\begin{figure}
  \begin{center}
    \includegraphics{example-mutation-sims/43099-r1-501-sb0_01-sm-0_01-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/69787-r1-501-sb0_01-sm-0_01-N600-pophistory-run}
    \includegraphics{example-mutation-sims/11821-r1-501-sb0_01-sm-0_01-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by new mutation
    with $s_m=0.01$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_2}
\end{figure}

% sm=0.001
\begin{figure}
  \begin{center}
    \includegraphics{example-mutation-sims/59611-r1-501-sb0_01-sm-0_001-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/93713-r1-501-sb0_01-sm-0_001-N600-pophistory-run}
    \includegraphics{example-mutation-sims/29850-r1-501-sb0_01-sm-0_001-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by new mutation
    with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_3}
\end{figure}

% sm=0.0001
\begin{figure}
  \begin{center}
    \includegraphics{example-mutation-sims/15449-r1-501-sb0_01-sm-1e-04-N1600-pophistory-run}
    \includegraphics{example-mutation-sims/5582-r1-501-sb0_01-sm-1e-04-N400-pophistory-run}
    \includegraphics{example-mutation-sims/24639-r1-501-sb0_01-sm-1e-04-N25-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by new mutation
    with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_4}
\end{figure}

% sm=0.1, R=80
\begin{figure}
  \begin{center}
    \includegraphics{example-migration-sims/89826-r1-501-sb0_01-sm-0_1-N4000-pophistory-run}
    \includegraphics{example-migration-sims/76178-r1-501-sb0_01-sm-0_1-N1000-pophistory-run}
    \includegraphics{example-migration-sims/95095-r1-501-sb0_01-sm-0_1-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by migration
    with $s_m=0.1$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_5}
\end{figure}

% sm=0.01, R=80
\begin{figure}
  \begin{center}
    \includegraphics{example-migration-sims/42080-r1-501-sb0_01-sm-0_01-N4000-pophistory-run}
    \includegraphics{example-migration-sims/82698-r1-501-sb0_01-sm-0_01-N1000-pophistory-run}
    \includegraphics{example-migration-sims/97545-r1-501-sb0_01-sm-0_01-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by migration
    with $s_m=0.01$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_6}
\end{figure}

% sm=0.001, R=80
\begin{figure}
  \begin{center}
    \includegraphics{example-migration-sims/88079-r1-501-sb0_01-sm-0_001-N4000-pophistory-run}
    \includegraphics{example-migration-sims/3464-r1-501-sb0_01-sm-0_001-N1000-pophistory-run}
    \includegraphics{example-migration-sims/37774-r1-501-sb0_01-sm-0_001-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by migration
    with $s_m=0.001$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_7}
\end{figure}

% sm=0.0001, R=80
\begin{figure}
  \begin{center}
    \includegraphics{example-migration-sims/26044-r1-501-sb0_01-sm-1e-04-N4000-pophistory-run}
    \includegraphics{example-migration-sims/85750-r1-501-sb0_01-sm-1e-04-N1000-pophistory-run}
    \includegraphics{example-migration-sims/4111-r1-501-sb0_01-sm-1e-04-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by migration
    with $s_m=0.0001$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_8}
\end{figure}

\ifsubmissionversion
\processdelayedfloats
\fi

>>>>

% make supp figures separate
\usepackage{caption}
\DeclareCaptionType{sfigure}[Figure]

@@

\ifsubmissionversion
    \usepackage[nolists,nomarkers,nohead]{endfloat}
    \usepackage{cite}
    \DeclareDelayedFloat{sfigure}[sss]{Supplementary Figure}
    % Use the PLoS provided bibtex style
    \bibliographystyle{plos2009}
    \newcommand{\citep}[1]{\cite{#1}}
    \newcommand{\citet}[1]{\cite{#1}}
\else
    \usepackage{natbib}
    \bibliographystyle{abbrvnat}
\fi

@@

% \pagestyle{myheadings}
%% ** EDIT HERE **

@@

%%%%%%%%%%%
\section*{Abstract}
Species often encounter, and adapt to, many patches of locally similar environmental conditions across their range. 
Such adaptation can occur through convergent evolution if different alleles arise and spread in different patches, 
or through the spread of shared alleles by migration
acting to synchronize adaptation across the species.
The tension between the two reflects 
the degree of constraint imposed on evolution by the underlying genetic architecture 
versus how effectively selection and geographic isolation act to inhibit the geographic spread of locally adapted alleles.
This paper studies a model of the balance between these two routes to adaptation in continuous environments with patchy selection pressures.
We address the following questions: 
How long does it take for a novel, locally adapted allele to appear in a
patch of habitat where it is favored through mutation?
Or, through migration from another, already adapted patch?
Which is more likely to occur, as a function of distance between the patches?
How can we tell which has occurred, i.e.\ what population genetic
signal is left by the spread of migrant alleles?
To answer these questions we examine the family structure underlying migration--selection equilibrium
surrounding an already adapted patch,
in particular treating those rare families that reach new patches
as spatial branching processes.
This provides a way to understand the role of geographic separation between patches 
in promoting convergent adaptation and the genomic signals it leaves behind.
We illustrate these ideas using the convergent evolution of cryptic coloration in the rock pocket mouse, \textit{Chaetodipus intermedius}, as an empirical example.

\section*{Author Summary}
Often, a large species range will include patches where the species differs because it has adapted to locally differing conditions.
For instance, rock pocket mice are often found with a coat color that matches the rocks they live in,
these color differences are controlled genetically,
and mice that don't match the local rock color are more likely to be eaten by predators.
Sometimes, similar genetic changes have occurred independently in different patches,
suggesting that there were few accessible ways to evolve the locally adaptive form.
However, the genetic basis could also be shared if
migrants carry the locally beneficial genotypes between nearby patches,
despite being at a disadvantage between the patches.
We use a mathematical model of random migration to determine how quickly adaptation is expected to occur 
through new mutation and through migration from other patches,
and study in more detail what we would expect successful migrations between patches to look like.
The results are useful for determining whether similar adaptations in different locations are likely to have the same genetic basis or not,
and more generally in understanding how species adapt to patchy, heterogeneous landscapes.

@@

@@

Here (and at other parameter choices) we see that the probability of establishment $p(x)$ goes to the equilibrium value
(approximately $p_e = 2s/\xi^2$) within the patch;
the transition is fairly symmetrical about the edge of the patch, even if the edge of the patch is not sharp.
Additional experimentation indicated that the fit remains equally good for other parameter values,
even if migration can move further than one deme and offspring numbers are not Poisson.
This lends credence to our approximation that the integral of $p(x)$ over the entire range
is close to $p_e$ multiplied by the area of the patch.

@@

\section*{Acknowledgements}
We would like to heartily thank Joachim Hermisson for a number of insightful suggestions,
and catching the algebra error present in the first version of this paper on the bioRxiv,
as well as the two anonymous reviewers.
We would also like to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.

@@

\ifsubmissionversion
\clearpage
\renewcommand*\listfigurename{Figure Legends}
\listoffigures
\fi

% endfloat uses different names
\ifsubmissionversion
  \renewcommand{\thesfigure}{S\arabic{sfigure}}
  \renewcommand{\thepostsfigure}{S\arabic{postsfigure}}
  % \renewcommand{\thefigure}{S\arabic{figure}}
  % \renewcommand{\thepostfigure}{S\arabic{postfig}}
  % \setcounter{postfig}{0}
  \renewcommand{\thetable}{S\arabic{table}}
  \renewcommand{\theposttable}{S\arabic{posttable}}
  \setcounter{posttable}{0}
\fi

%% list of supplementary figures
\ifsubmissionversion
  \renewcommand*\listsfigurename{Supplementary Figure Legends}
  \listofsfigures
  \renewcommand*\listtablename{Supplementary Table Legends}
  \listoftables
  \pagebreak
\fi

\appendix
\section{Supporting Information}

@@

%%%%%%%
\subsection{The exact solution to the equilibrium frequency}
\label{apx:elliptic_integrals}

@@

%%%%%%%
\subsection{More information about the simulations}
\label{apx:parameter_tables}

@@

%%%
% Tables

@@

%%%
% Supplementary Figures

\begin{sfigure}
  \begin{center}
    \includegraphics{mutation-times-predicted}
  \end{center}
  \caption{
    The same data shown in the left panel of figure~\ref{fig:sim_times},
    but all times shown (not just the interquartile ranges),
    and including those parameter values at which most of the simulations did not adapt by 25,000 generations.
  } \label{sfig:sim_migration_times}
\end{sfigure}

\begin{sfigure}
  \begin{center}
    \includegraphics{migration-time-predicted}
  \end{center}
  \caption{
    The same data shown in the right panel of figure~\ref{fig:sim_times},
    but all times shown (not just the interquartile ranges),
    and including those parameter values at which most of the simulations did not adapt by 25,000 generations.
    The upper panel has the predicted time to adaptation on the horizontal axis as in figure~\ref{fig:sim_times},
    and the lower panel has, for comparison, the raw distance between patches 
    (which predicts time to adaptation, but not as well).
  } \label{sfig:sim_mutation_times}
\end{sfigure}

@@

% sm=0.1
\begin{sfigure}
  \begin{center}
    \includegraphics{example-mutation-sims/18885-r1-501-sb0_01-sm-0_1-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/56325-r1-501-sb0_01-sm-0_1-N600-pophistory-run}
    \includegraphics{example-mutation-sims/28432-r1-501-sb0_01-sm-0_1-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by new mutation
    with $s_m=0.1$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_1}
\end{sfigure}

% sm=0.01
\begin{sfigure}
  \begin{center}
    \includegraphics{example-mutation-sims/43099-r1-501-sb0_01-sm-0_01-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/69787-r1-501-sb0_01-sm-0_01-N600-pophistory-run}
    \includegraphics{example-mutation-sims/11821-r1-501-sb0_01-sm-0_01-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by new mutation
    with $s_m=0.01$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_2}
\end{sfigure}

% sm=0.001
\begin{sfigure}
  \begin{center}
    \includegraphics{example-mutation-sims/59611-r1-501-sb0_01-sm-0_001-N1200-pophistory-run}
    \includegraphics{example-mutation-sims/93713-r1-501-sb0_01-sm-0_001-N600-pophistory-run}
    \includegraphics{example-mutation-sims/29850-r1-501-sb0_01-sm-0_001-N50-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by new mutation
    with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_3}
\end{sfigure}

% sm=0.0001
\begin{sfigure}
  \begin{center}
    \includegraphics{example-mutation-sims/15449-r1-501-sb0_01-sm-1e-04-N1600-pophistory-run}
    \includegraphics{example-mutation-sims/5582-r1-501-sb0_01-sm-1e-04-N400-pophistory-run}
    \includegraphics{example-mutation-sims/24639-r1-501-sb0_01-sm-1e-04-N25-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by new mutation
    with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_4}
\end{sfigure}

% sm=0.1, R=80
\begin{sfigure}
  \begin{center}
    \includegraphics{example-migration-sims/89826-r1-501-sb0_01-sm-0_1-N4000-pophistory-run}
    \includegraphics{example-migration-sims/76178-r1-501-sb0_01-sm-0_1-N1000-pophistory-run}
    \includegraphics{example-migration-sims/95095-r1-501-sb0_01-sm-0_1-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by migration
    with $s_m=0.1$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_5}
\end{sfigure}

% sm=0.01, R=80
\begin{sfigure}
  \begin{center}
    \includegraphics{example-migration-sims/42080-r1-501-sb0_01-sm-0_01-N4000-pophistory-run}
    \includegraphics{example-migration-sims/82698-r1-501-sb0_01-sm-0_01-N1000-pophistory-run}
    \includegraphics{example-migration-sims/97545-r1-501-sb0_01-sm-0_01-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by migration
    with $s_m=0.01$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_6}
\end{sfigure}

% sm=0.001, R=80
\begin{sfigure}
  \begin{center}
    \includegraphics{example-migration-sims/88079-r1-501-sb0_01-sm-0_001-N4000-pophistory-run}
    \includegraphics{example-migration-sims/3464-r1-501-sb0_01-sm-0_001-N1000-pophistory-run}
    \includegraphics{example-migration-sims/37774-r1-501-sb0_01-sm-0_001-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by migration
    with $s_m=0.001$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_7}
\end{sfigure}

% sm=0.0001, R=80
\begin{sfigure}
  \begin{center}
    \includegraphics{example-migration-sims/26044-r1-501-sb0_01-sm-1e-04-N4000-pophistory-run}
    \includegraphics{example-migration-sims/85750-r1-501-sb0_01-sm-1e-04-N1000-pophistory-run}
    \includegraphics{example-migration-sims/4111-r1-501-sb0_01-sm-1e-04-N100-pophistory-run}
  \end{center}
  \caption{
    Randomly chosen simulations of adaptation by migration
    with $s_m=0.0001$, $R=80$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left);
    dotted black lines indicate the patches where $B$ is advantageous.
  } \label{sfig:sims_8}
\end{sfigure}
